Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
explicite difference
phrase plus jolie

Guided static analysis \cite{DBLP:conf/sas/GopanR07} applies to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}, except
that we call the abstract values $X_i^s$ instead of $X_i$ to leave room for
another abstract value $X_i^d$ later in the algorithm.

@@

The algorithm for Guided static analysis on the implicit multigraph is described
in Algorithm \ref{algo:combined}.

>>>>

Guided static analysis, as proposed by \citet{DBLP:conf/sas/GopanR07}, applied to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}, except
that we call the abstract values $X_i^s$ instead of $X_i$ to leave room for
another abstract value $X_i^d$ later in the algorithm.

@@

Algorithm~ \ref{algo:combined} performs Guided static analysis on the implicitly represented multigraph.
